\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based TSDF Calculation

### 2024-03-17 Articles/IROS/root.tex
edited rotational velocities

Prioritizing control over the end-effector's (EE) translational velocity is essential for a consistent and stable target approach. The commonly used method, where translational velocity is proportional to squared distance, leads to impractically high initial velocities, which can prevent obstacle avoidance and real-world execution, followed by disproportionately slow velocities when nearing the goal position. Our aim is a consistent velocity profile throughout the trajectory, with controlled deceleration near the goal. This is achieved by first calculating the unit vector towards the target for direction, then modulating its magnitude using a sigmoid function, specifically the arctangent function (Eq. \ref{eq: v_att}).

@@

The rotational velocity error of the EE is needed for ensuring goal orientation of the EE. In our approach, orientations are depicted using rotation matrices. Specifically, \( R \) represents the current EE orientation, while \( gR \) signifies the goal EE orientation. The disparity between these orientations is encapsulated by the relative rotation matrix \( dR \). This matrix is formulated by multiplying the goal orientation matrix \( gR \) with the transpose of the current orientation matrix \( cR^{T} \). To ensure that it represents a pure rotation without any scaling we than normalize the so gotten matrix .

\begin{equation}
	dR = \frac{gR \cdot cR^{T}}{||gR \cdot cR^{T}||}
	\label{eq: rot_diff_mat}
\end{equation}

The relative rotation matrix value is converted into a quaternion, which is then logarithmically transformed \remove{to represent the rotational error vectorially}. The components of this quaternion, excluding the real part, than form the rotational error vector \( \omega \).

\begin{equation}
	dR \mapsto dQ = a + b \, i + c \, j + d \, k
	\label{eq: quat_mapsto}
\end{equation}

\begin{equation}
	dQl = 2 \cdot \log(dQ) = al + bl \, i + cl \, j + dl \, k
	\label{eq:quat_log}
\end{equation}

\alert{There needs to be an explanation why log, where is this from. Maybe a reference. cite: DMP Quaternions article Petrič, Žlajpah, Ude}

\begin{equation}
	\vec{\omega} =
	\begin{bmatrix}
		bl \\
		cl \\
		dl
	\end{bmatrix}
	\label{eq:rot_error_vector}
\end{equation}

To get the full velocity of the end effector (EE), \( \mathrm{\vec{v}_{ATT}} \), we combines translational and rotational velocities, which we scale using proportional gains \( k_p \) and \( k_r \).

\begin{equation}
	\mathrm{\vec{v}_{att}} = 
	\begin{bmatrix}
		k_pv* \vec{v}   \\
		k_{\omega} * \vec{\omega}
	\end{bmatrix}
	\label{eq:ee_velocity}
\end{equation}

@@

\add{TODO}

>>>>

Prioritizing control over the end-effector's (EE) translational velocity is essential for a consistent and stable target approach. The commonly used method, where translational velocity is proportional to squared distance, leads to impractically high initial velocities, which can prevent obstacle avoidance and real-world execution, followed by disproportionately slow velocities when nearing the goal position. Our aim is a consistent velocity profile throughout the trajectory, with controlled deceleration near the goal. This is achieved by first calculating the unit vector towards the target for direction, then modulating its magnitude using a sigmoid function, specifically the arctangent function (eq. \ref{eq: v_att}).

@@

%The rotational error of the EE is needed for ensuring goal orientation of the EE. In our approach, orientations are depicted using rotation matrices. Specifically, \( R \) represents the current EE orientation, while \( gR \) signifies the goal EE orientation. The disparity between these orientations is encapsulated by the relative rotation matrix \( dR \). This matrix is formulated by multiplying the goal orientation matrix \( gR \) with the transpose of the current orientation matrix \( cR^{T} \). To ensure that it represents a pure rotation without any scaling we than normalize the so gotten matrix .

%Determination of the requisite rotation adjustment utilizes the relative rotation matrix \(dR\), calculated from the multiplication of \(gR\) by the \(cR\) transpose, and subsequent normalization to ensure a pure rotational representation. This method guarantees that \(dR\) accurately captures the orientation discrepancy, devoid of any scaling factor.

%The current orientation of the end-effector (EE) and its goal orientation are encoded through rotation matrices, \(cR\) for the current state and \(gR\) for the goal state. The necessary rotational adjustment is identified through the relative rotation matrix \(dR\), generated by multiplying \(gR\) with the transpose of \(cR\) and then normalizing the outcome (eq. \ref{eq: rot_diff_mat}). This process ensures \(dR\) accurately represents rotational differences, without any scaling factors.
%
%To enhance computational efficiency and prevent gimbal lock, the approach transitions from matrix to quaternion representations for precise and efficient rotational velocity adjustments, essential for achieving the target orientation of the EE.

The current orientation of the end-effector (EE) and its goal orientation are encoded through rotation matrices, \(\mathbf{cR}\) for the current state and \(\mathbf{gR}\) for the goal state. The necessary rotational adjustment is identified through the relative rotation matrix \(\mathbf{dR}\), generated by multiplying \(\mathbf{gR}\) with the transpose of \(\mathbf{cR}\) and then normalizing the outcome (eq. \ref{eq: rot_diff_mat}). This process ensures \(\mathbf{dR}\) accurately represents rotational differences, without the effect of any scaling factors.

%\begin{equation}
%	dR = \frac{gR \cdot cR^{T}}{||gR \cdot cR^{T}||}
%	\label{eq: rot_diff_mat}
%\end{equation}

%\begin{equation}
%	\boldsymbol{dR} = \frac{\boldsymbol{gR} \cdot \boldsymbol{cR}^{T}}{\left\lVert\boldsymbol{gR} \cdot \boldsymbol{cR}^{T}\right\rVert}
%	\label{eq: rot_diff_mat}
%\end{equation}

\begin{equation}
	\mathbf{dR} = \frac{\mathbf{gR} \cdot \mathbf{cR}^{T}}{||\mathbf{gR} \cdot \mathbf{cR}^{T}||}
	\label{eq: rot_diff_mat}
\end{equation}

To enhance computational efficiency and prevent gimbal lock, the approach transitions from matrix to quaternion representations for precise and efficient rotational velocity adjustments, essential for achieving the target orientation of the EE.

The relative rotation matrix is converted into a quaternion, which is subsequently logarithmically transformed. The resulting quaternion's components, excluding the real part, constitute the rotational error vector \( \vec{\omega} \).
%
%\begin{equation}
%	dR \mapsto dQ = a + b \, i + c \, j + d \, k
%	\label{eq: quat_mapsto}
%\end{equation}
%
%\begin{equation}
%	dQl = 2 \cdot \log(dQ) = al + bl \, i + cl \, j + dl \, k
%	\label{eq:quat_log}
%\end{equation}

\begin{equation}
	\boldsymbol{dR} \mapsto \boldsymbol{dQ} = a + b \, \vec{i} + c \, \vec{j} + d \, \vec{k}
	\label{eq: quat_mapsto}
\end{equation}

\begin{equation}
	\boldsymbol{dQl} = 2 \cdot \log(\boldsymbol{dQ}) = a_{log} + b_{log} \, \vec{i} + c_{log} \, \vec{j} + d_{log} \, \vec{k}
	\label{eq:quat_log}
\end{equation}

\alert{There needs to be an explanation why log, cite: DMP Quaternions article Žlajpah, Ude}

\begin{equation}
	\vec{\omega} =
	\begin{bmatrix}
		b_{log} \\
		c_{log} \\
		d_{log}
	\end{bmatrix}
	\label{eq:rot_error_vector}
\end{equation}

To get the full velocity of the end effector (EE), \( \mathrm{\vec{v}_{att}} \), we combines translational and rotational velocities, which we scale using proportional gains \( k_v \) and \( k_\omega \).

\begin{equation}
	\mathrm{\vec{v}_{att}} = 
	\begin{bmatrix}
		k_{v} * \vec{v}   \\
		k_{\omega} * \vec{\omega}
	\end{bmatrix}
	\label{eq:ee_velocity}
\end{equation}

@@
